### 2016-07-15 version0.0/asli.tex
finishing intro0.0
finishing edits on intro
Adding summary

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% University of Western Ontario Thesis Template
% By: Justin Quinn Veenstra, 2010
% With thanks to Mr. (soon to be Dr.) Will Robertson.

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
\usepackage{hyperref} %comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}
\usepackage{chapterbib}
\usepackage{mwe}    % loads »blindtext« and »graphicx«
\usepackage{subfig}

\makeatletter
\numberwithin{figure}{chapter}
\newenvironment{acknowledgements}%
{\clearemptydoublepage
 \begin{center}
  \section*{Acknowledgements}
 \end{center}
 \begingroup
}{\newpage\endgroup}

@@

%% To produce output with the desired line spacing, the argument of
%% \spacing should be multiplied by 5/6 = 0.8333, so that 1 1/2 spaced
%% corresponds to \spacing{1.5} and double spaced is \spacing{1.66}.
\def\normalspacing{1.25} % default line spacing

@@

\setcounter{tocdepth}{3} % Number the subsubsections 
\def\normalspacing{1.25} % default line spacing

@@

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. M. Daley}
\newcommand{\examth}{Dr. S. C. Gallagher}
\newcommand{\examf}{Dr. P. Wiegert}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
\newcommand{\spinetitle}{Extragalactic star formation}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
Thanks to Sophia, Hossein and Els. 
}
\newcommand{\makeacknowlege} { 1) Pauline
2) Els, Sophia, Hossein,
3)I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam, Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
4) bacheha
5) western ppl; Jodi, Brian, Henry, Phin,...
6) Mohad, shahin, pejman, pouria, masood,babak
7) fako famil
}
\newcommand{\makededications} {
To my parents, my sisters, and Matin, for their unconditional love and support. 
}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

@@

\vfill
\begin{table}[ht]
\begin{minipage}[t]{0.5\linewidth} %tabular instead?
\begin{tabular}{l}
\underline{Supervisor:}\vspace{0.35in}
\isdefinedsig{\super}
\isco{\superc}
\isjoint{\superj}
\isalt{\supera}
\underline{Supervisory Committee:}\vspace{0.35in}
\isdefinedsig{\sco}\vspace{0.15in}
\isdefinedsig{\sct}
\end{tabular}
\vfill
\end{minipage}
\hspace{0.5in}
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{l}
\underline{Examiners:} \\\vspace{.5cm}
\isdefinedsig{\examo}\\
\isdefinedsig{\examt}\\
\isdefinedsig{\examth}\\
\isdefinedsig{\examf}
\end{tabular}
\vfill
\end{minipage}
\vfill
\end{table}
\vfill
\begin{center}
The thesis by \\ \vfill
\textbf{\firstname{} \middlename{} \underline{\lastname}}\\
\vfill
entitled:\\\vfill
\textbf{\titl}\\\vfill
is accepted in partial fulfillment of the \\
requirements for the degree of\\
\degree\\
\end{center}
\begin{table}[ht]
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{l}
\dots\dots\dots\dots\dots\\
Date
\end{tabular}
\end{minipage}
\hspace{0.5in}
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{l}
\dots\dots\dots\dots\dots\dots\dots\dots\dots\dots\\
Chair of the Thesis Examination Board
\end{tabular}
\end{minipage}
\end{table}

@@

\makeatother
\begin{document}

%% ***   NOTE   ***
%% You should put all of your '\newcommand', '\newenvironment', and
%% '\newtheorem's (in other words, all the global definitions that you
%% will need throughout your thesis) in a separate file and use
%% "\input{filename}" to input it here.

\newcommand \kpc {\,{\rm kpc}}
\newcommand \sigmagas {$\Sigma_{\mathrm {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
\newcommand \eqsigmagas {\Sigma_{\mathrm {gas }}}
\newcommand \sigmasfr {$\Sigma_{\mathrm {SFR }} $\ }
\newcommand \eqsigmasfr {\Sigma_{\mathrm {SFR }}}
\newcommand \sigmastar {$\Sigma_{\mathrm {star }} $\ }
\newcommand \eqsigmastar {\Sigma_{\mathrm {star }}}
\newcommand \halpha {H$\alpha $\ }
\newcommand \um {$\mu$m\ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~{\textsc II}]} 
\newcommand \oiii {[O~{\textsc III}]} 
\newcommand \hi {H~{\textsc I}}
\newcommand \hii {H~{\textsc II}}
\newcommand \oii {[O~{\textsc II}]}
\newcommand \nii {[N~{\textsc II}]}

@@

%% This sets the page style and numbering for preliminary sections.
\begin{preliminary}
\defcitealias{Hossein12}{T12}
\defcitealias{Kinney96}{K96}
\defcitealias{Noll09}{N09}

@@

\include{intro0.0}
%\include{paper1}
%\include{paper3}
%\include{paper2}

%% This adds a line for the Bibliography in the Table of Contents.
%\addcontentsline{toc}{chapter}{Bibliography}
%% ***   Set the bibliography style.   ***
%\bibliographystyle{apj.bst} % (change according to your preference)
%%% ***   Set the bibliography file.   ***
%\bibliography{westernthesis}

%Appendices.
\begin{appendices}
\include{appendixa}
\end{appendices}

>>>>

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
\usepackage{hyperref} %comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}
\usepackage{chapterbib}
\makeatletter
\numberwithin{figure}{chapter}
\newenvironment{acknowledgements}%
{\clearemptydoublepage
 \begin{center}
  \section*{Acknowledgements}
 \end{center}
 \begingroup
}{\newpage\endgroup}

@@

%% To produce output with the desired line spacing, the argument of
%% \spacing should be multiplied by 5/6 = 0.8333, so that 1 1/2 spaced
%% corresponds to \spacing{1.5} and double spaced is \spacing{1.66}.
\def\normalspacing{1.5} % default line spacing

@@

\setcounter{tocdepth}{3} % Number the subsubsections 
\def\normalspacing{1.5} % default line spacing

@@

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. M. Daley}
\newcommand{\examth}{Dr. S. C. Gallagher}
\newcommand{\examf}{Dr. P. Wiegert}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
%\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
\newcommand{\spinetitle}{Extragalactic Star Formation}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
The work presented in this thesis has greatly benefited from advice by my supervisor Dr. Pauline Barmby and collaborators: Dr. Sofia Lianue, Dr. Hossein Teimoorinia, and Dr. Els Peeters. Although I led the projects, performed the analysis and wrote the manuscripts, their suggestions and feedback on the analyses and manuscripts were greatly helpful.

{\bf Chapter 2}: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in the Monthly Notices of the Royal Astronomical Society, Volume 456, Issue 4, 2016.

{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future.

{\bf Chapter 4}: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to The Monthly Notices of The Royal Astronomical Society.
}

\newcommand{\makeacknowlege} { 1) Pauline
2) Els, Sophia, Hossein,
3)I would like to thank all my Friends in Western. Neven, dave, Matt, parshati, sina, zahra, fereshteh, aycha, maryam(s) , Laura, Taylor, dimuthu, Sham, ghazal, pubu, robin, Hoori, Javad, ali, shanon, Mohad, Boshra
4) bacheha
5) western ppl; Jodi, Brian, Henry, Phin,...
6) Mohad, shahin, pejman, pouria, masood,babak
7) fako famil
}
\newcommand{\makededications} {

\emph{To my parents, my sisters,}

\emph{\& Matin,}

\emph{for their unconditional love and support.}

}
\newcommand{\listappendixname}{List of Appendices}
\newlistof{myappendices}{app}{\listappendixname}
\newcommand{\myappendices}[1]{%
\addcontentsline{app}{myappendices}{#1}\par}

@@

\vfill
\begin{table}[ht]
\begin{minipage}[t]{0.5\linewidth} %tabular instead?
\begin{tabular}{l}
\underline{Supervisor:}\vspace{0.35in}
\isdefinedsig{\super}\\
\underline{Supervisory Committee:}\vspace{0.35in}
\isdefinedsig{\sco}\vspace{0.15in}
\isdefinedsig{\sct}
\end{tabular}
\vfill
\end{minipage}
\hspace{0.5in}
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{l}
\underline{Examiners:} \\\vspace{.5cm}
\isdefinedsig{\examo}\\
\isdefinedsig{\examt}\\
\isdefinedsig{\examth}\\
\isdefinedsig{\examf}
\end{tabular}
\vfill
\end{minipage}
\vfill
\end{table}
\vfill
\begin{center}
The thesis by \\ \vfill
\textbf{\firstname{} \middlename{} \underline{\lastname}}\\
\vfill
entitled:\\\vfill
\textbf{\titl}\\\vfill
is accepted in partial fulfillment of the \\
requirements for the degree of\\
\degree\\
\end{center}
\begin{table}[ht]
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{l}
\dots\dots\dots\dots\dots\\
Date
\end{tabular}
\end{minipage}
\hspace{0.5in}
\begin{minipage}[t]{0.5\linewidth}
\begin{tabular}{l}
\dots\dots\dots\dots\dots\dots\dots\dots\dots\dots\\
Chair of the Thesis Examination Board
\end{tabular}
\end{minipage}
\end{table}

@@

\makeatother
\begin{document}
%% ***   NOTE   ***
%% You should put all of your '\newcommand', '\newenvironment', and
%% '\newtheorem's (in other words, all the global definitions that you
%% will need throughout your thesis) in a separate file and use
%% "\input{filename}" to input it here.

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\mathrm{gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\mathrm {total\, gas }} $\ }
\newcommand{\eqsigmagas}    {\Sigma_{\mathrm {gas }}}
\newcommand{\sigmasfr}   {$\Sigma_{\mathrm {sfr }} $\ }
\newcommand{\eqsigmasfr}{\Sigma_{\mathrm{sfr }}}
\newcommand{\sigmastar}    {$\Sigma_{\mathrm {star }} $\ }
\newcommand{\eqsigmastar}    {\Sigma_{\mathrm {star }}}
\newcommand{\halpha}    {H$\alpha $\ }
\newcommand{\um}    {$\mu$m\ }
\newcommand{\mice} {$\mu$m}
\newcommand{\nprime}{N$^\prime$}
\newcommand{\eqnprime} {N^\prime}
\newcommand{\degr} {$^{\circ}$}
\newcommand{\arcmin} {$^{\prime}$}
\newcommand {\arcsec} {$^{\prime\prime}$}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \Galex {GALEX\ }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~{\textsc ii}]} 
\newcommand \oiii {[O~{\textsc iii}]} 
\newcommand \hi {H~{\textsc i}}
\newcommand \hii {H~{\textsc ii}}
\newcommand \oii {[O~{\textsc ii}]}
\newcommand \nii {[N~{\textsc ii}]}

@@

\defcitealias{Hossein12}{T12}
\defcitealias{Kinney96}{K96}
\defcitealias{Noll09}{N09}
%% This sets the page style and numbering for preliminary sections.
\begin{preliminary}

@@

\include{intro0.0}
\include{paper1}
\include{paper3}
\include{paper2}
\include{summary}

%% This adds a line for the Bibliography in the Table of Contents.
% \addcontentsline{toc}{chapter}{Bibliography}
% %% ***   Set the bibliography style.   ***
% \bibliographystyle{apj.bst} % (change according to your preference)
% %%% ***   Set the bibliography file.   ***
% \bibliography{western_bib}

% \addcontentsline{toc}{section}{Bibliography}
% \bibliographystyle{apj.bst}
% \bibliography{western_bib.bib}

%Appendices.

% %Appendices.
\begin{appendices}
\include{appendixa}
\include{appendixb}
\include{appendixc}
\end{appendices}
